---
title: "Linear Regression Analysis"
---

We first read the data into R. Use the function str( ) to find the structure of the data frame and the summary( ) to summarize the data. We then create a new variable called “logSales”, which is the logarithm of the variable “Sales” in the data frame “walmart”. 

```{r}
data <- read.csv("Walmart_Data.csv")
str(data)
```
```{r}
summary(data)
```
```{r}
data$logSales = log(data$Sales)
head(data)
```
We then use the correlation function cor( ) to find the pairwise correlation between the three variables, “Sales”, “Promotion” and “Feature”
```{r}
cor(data[ , 2:4])
```
```{r}
library(ggplot2)
```
Scatterplots can be used for visually presenting the relationships.
```{r}
plot(data$Promotion,data$Sales)
```
```{r}
plot(data$Feature,data$Sales)
```
```{r}
hist(data$Sales)
```
```{r}
hist(data$logSales)
```
```{r}
library(stats)
```
We will now run a regression to see how the dependent variable logsales are impacted by a variety of factors. 
```{r}
lm_model<- lm(data$logSales~data$Promotion+data$Feature+data$Walmart+data$Holiday)
```
```{r}
summary(lm_model)
```
B1 is 0.84754, indicating that an increase in promotions by 1 will lead to 0.84754 more log sales. Additionally, because there is a P-value of 8.48e-05, which is less than 0.05, the difference is statistically significant. 

B2 is 0.75076, indicating that an increase in feature advertising by 1 will lead to 0.75076 more log sales. Additionally, because there is a P-value of 0.000485, which is less than 0.05, the difference is statistically significant. 

B3 is -0.31127, indicating that the presence of Walmart will lead to a decrease in log sales by 0.31127 than when there is not a Walmart. Additionally, because there is a P-value of 6.76e-11, which is less than 0.05, the difference is statistically significant. 

B4 is 0.26004, indicating that when there is a holiday, there is 0.26004 more log sales than when there is not a holiday. Additionally, because there is a P-value of 0.001164, which is less than 0.05, the difference is statistically significant. 

So can we conclude the entry of Wal-mart affects the sales of the local store?

Yes, we can. We see that after Walmart is present, log sales decrease by 0.31127 based on this regression model. This coefficient is also statistically significant given an incredibly low P-value of 6.76e-11. Therefore, we conclude that the entry of Walmart decreases sales. 

We now incorporate interaction effects.
```{r}
lm_model2<- lm(data$logSales~data$Promotion+data$Feature+data$Walmart+data$Holiday+data$Holiday:data$Walmart+data$Holiday:data$Promotion)
```
```{r}
summary(lm_model2)
```
B1 is 0.7454. This means whenever there is an increase in promotions by 1, there is an increase in log sales by 0.7454. This is a statistically significant increase given a small P- value of 0.00123, which is below 0.05. 

B2 is 0.7828. This means whenever there is an increase in feature advertising by 1, there is an increase in log sales by 0.7828. This is a statistically significant increase given a small P-value of 0.00033, which is below 0.05. 

B3 is -0.2978, indicating that the presence of Walmart will lead to a decrease in log sales by 0.2978 than when there is not a Walmart. Additionally, because there is a P-value of 1.08e-09, which is less than 0.05, the difference is statistically significant. 

B4 is -0.1128 indicating that when there is a holiday, there is 0.1128 less log sales than when there is not a holiday. However, because the P-value is quite large at 0.87961, the difference is not statistically significant. 

B5 is -0.1307 indicating that when there is both a Walmart present and a holiday, there is 0.1307 less log sales than when there is not both a Walmart and a holiday present. However, because the P-value is quite large at 0.49034, the difference is not statistically significant. 

B6 is 0.4330 indicating that when there is a holiday and promotions go up by 1, there is 0.4330 more log sales than when there is not a holiday and promotions do not go up by 1. However, because the P-value is quite large at 0.52219, the difference is not statistically significant. 

We can compare this model with the previous one using AIC and BIC.
```{r}
AIC(lm_model)
```
```{r}
AIC(lm_model2)
```
```{r}
BIC(lm_model)
```
```{r}
BIC(lm_model2)
```
Model A (the model in Question 3) is the better model under both AIC and BIC. We see that Model A has a smaller AIC (-21.45434 versus -19.48443) as well as a lower BIC (- 5.823324 versus 1.356929). Therefore, we can conclude Model A is preferable. 



